Cover Sheet
========================================================


By including this statement, we, all the students listed in the table
below, declare that:

- We hold a copy of this assignment if the original is lost or damaged.

- We hereby certify that no part of this assignment has been copied from
  any other student's work or from any other source except where due
  acknowledgement is made in the assignment.

- No part of the assignment has been written for us by any other person
  except where collaboration has been authorised by the unit coordinator.

- We are aware that this work may be reproduced and submitted to plagiarism
  detection software programs for the purpose of detecting possible
  plagiarism; this software may retain a copy on its database for future
  plagiarism checking.

- We hereby certify that no part of this assignment or product has been
  submitted by any of us in another (previous or current) assessment, except
  where appropriately referenced, and with prior permission from the unit
  coordinator for this unit.

- We hereby certify that we have read and understand what the University
  considers to be academic misconduct, and that we are aware of the
  penalties that may be imposed for academic misconduct.

Name               | Student Number | Contribution (%)
-------------------|----------------|-----------------
Rachel Hardie      |18820821        |
                   |                |
                   |                |
                   |                |

<div style="page-break-before:always;"></div>


Group Project
========================================================

This Group Project analyses hard drive reliability data.
The file HardDisks.csv contains the following information for 125864 hard drives:
(1) a unique serial number;
(2) the model of the hard drive;
(3) the number of days the hard drive was operational;
(4) the mean operating temperature of the drive; and
(5) whether the hard drive was removed because it had failed.
A drive that is listed as not having failed either was still operational at the end of the data collection period, or it was
removed for other reasons, for instance a capacity upgrade.


Part One - Proportion of drives that fail early
--------------------------------------------------------

We want to investigate the proportion of drives that fail in the first year of operation.
(a) [1 mark] Create a subset of the cases that is relevant for this analysis and print the number of cases in that subset.


```{r}
drives = read.csv("HardDisks.csv",header=TRUE) #Load a dataset from .csv file
attach(drives)
drives.failed=which(failed=="TRUE")
length(drives.failed)
```
(b) [1 mark] Compute a point estimate for the proportion of drives that fail in the first year of operation.

```{r}

```


(c) [2 marks] Use bootstrapping to compute a 99% confidence interval for the proportion of drives that fail in the first
year of operation

